Citation Analysis of Computer Science

### 2019-11-13 Scientometrics/comp.tex
update

Progressing beyond the triad of theoretical foundations; hardware and computer systems; and software, the Computing Classification System (CCS) published by the Association for Computing Machinery (ACM) now consists of 13 top-level areas. https://dl.acm.org/ccs/ccs.cfm \emph{need to figure out to put this in BibTeX} that reflect a more current view of the field. This classification addresses relationships with other fields under Applied Computing. However, an easy way to map scientific publications, especially interdisciplinary articles or those from adjacent fields, to the CCS classification does not exist. Other classification systems exist such as the All Science Journal Classification (ASJC) developed and maintained by Scopus. the Web of Science Subject Classification System, and the NSF classification system. All three rely on applying one or more journal-derived labels to articles. Limitations of journal based classification have stimulated efforts to use article level clusters using citations and text similarity for links. \emph{cite Boyack, Small, Waltman, etc,}. These limitations are well known~\emph{wang and waltman; lariviere paper} and efforts have been made to instead build article level clusters using citations or other criteria for assembly .
\emph{https://www.nsf.gov/statistics/nsf13327/pdf/tabb1.pdf}, WoS \\ 
\emph{https://bit.ly/2NBRqaH}, and the  
\\ \emph{insert url} are based on journals that rely on assigning journal-level labels to articles.

In this article, we attempt to provide explore the structure of computer science through matching records from two major data sources. (i) the dblp bibliography- a reference bibliography for computer science\emph{cite} (ii) the Scopus bibliography, which covers the physical science, life sciences, social sciences, and health sciences. Using direct citations and co-citations as links, we construct clusters of articles that are drawn from journals and conference proceedings  and reconcile them with the All Science Journal Classification (ASJC) developed and maintained by Scopus.

@@

>>>>

Progressing beyond the triad of theoretical foundations; hardware and computer systems; and software, the Computing Classification System (CCS) published by the Association for Computing Machinery (ACM) now consists of 13 top-level areas. https://dl.acm.org/ccs/ccs.cfm \emph{need to figure out to put this in BibTeX} that reflect a more current view of the field. This classification addresses relationships with other fields under Applied Computing. However, an easy way to map scientific publications, especially interdisciplinary articles or those from adjacent fields, to the CCS classification does not exist. Other classification systems exist such as the All Science Journal Classification (ASJC) developed and maintained by Scopus. the Web of Science classification of research areas, and the NSF classification system. All three rely on applying one or more journal-derived labels to articles. Limitations of journal based classification have stimulated efforts to use article level clusters using citations and text similarity for links. \emph{cite Boyack, Small, Waltman, etc,}. These limitations are well known~\emph{wang and waltman; lariviere paper} and efforts have been made to instead build article level clusters using citations or other criteria for assembly .
\emph{https://www.nsf.gov/statistics/nsf13327/pdf/tabb1.pdf}, WoS \\ 
\emph{https://bit.ly/2NBRqaH}, and the  
\\ \emph{insert url} are based on journals that rely on assigning journal-level labels to articles.

In this article, we explore the structure of computer science through matching records from two major data sources. (i) the dblp bibliography- a reference bibliography for computer science\emph{cite} (ii) the Scopus bibliography, which covers the physical science, life sciences, social sciences, and health sciences. Using direct citations and co-citations as links, we then construct clusters of articles that are drawn from journals and conference proceedings  and reconcile them with the All Science Journal Classification (ASJC) developed and maintained by Scopus.

@@

\begin{figure}[ht]
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.5]{scopus_dblp_graclus2.pdf}
% figure caption is below the figure
\caption{insert caption}
\label{heatmap}       % Give a unique label
\end{figure}
